---
title: "Homework 2"
author: "Samruddhi Shinde"
date: "2/7/2021"
output:
  html_document: default
  github_document: default
---

<!-- BMW: When you submit your homework, you need to knit it twice by clicking the Knit button in RStudio. Once to github_document and once to html_document. -->

# Exercise 1

<!-- BMW: You need a space after # in headings -->

## 1.1 

Loading in packages needed for assignments

<!-- BMW: You need a blank line between paragraphs in markdown. A single line break is ignored. -->

```{r setup, include = FALSE}
# BMW: Name the chunk at the top where you load your packages 'setup'
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gapminder)
library(palmerpenguins) # BMW: You only need to library() a package once in a script.
```

Filter data set to show 3 countries (Mexico, Pakistan, & Zimbabwe) from the 1970s

```{r}
gapminder %>%
  filter(country %in% c("Mexico","Pakistan", "Zimbabwe") & year %in% c(1970:1979))
```

## 1.2

Select country and gdpPercap from filtered dataset

```{r}
gapminder %>%
  filter(country %in% c("Mexico","Pakistan", "Zimbabwe") & year %in% c(1970:1979)) %>%
  select(country, gdpPercap)
```

## 1.3 

Create new variable for thr change in life expectancy

```{r}
gapminder %>%
  group_by(country) %>% 
  mutate(change_in_lifeExp = lifeExp - lag(lifeExp)) %>%
  filter(change_in_lifeExp < 0)
```

<!-- BMW: Good job! You need to group by country so that you don't subtract the 2007 value for one country from the 1952 value from the next country. -->

## 1.4

Filter gapminder dataset to show the max GDP per capita for each country

```{r}
gapminder %>%
  group_by(country) %>%
  filter(gdpPercap == max(gdpPercap))
```

<!-- BMW: Great work! -->

## 1.5

Scatter plot of Canada's Life expectancy vs GDP per capita

```{r}
gapminder %>%
  filter(country == "Canada") %>%
  ggplot +
    aes(x = gdpPercap, y = lifeExp) +
    geom_point() + 
    scale_x_log10("GDP per capita", labels = scales::dollar_format()) +
    ylab("Life Expectancy") +
    ggtitle("Canada's GDP per Capita vs Life Expectancy")
```

<!-- BMW: Very nice! -->

# Excerise 2

## 2.1

Loading in packages for exercise 

```{r}
# BMW: Put all library() calls at the top of your script.
```

Summarize bill length and bill depth

```{r}
palmerpenguins::penguins %>%
  summarize(
    across(
      c(bill_length_mm, bill_depth_mm),
      list(
        mean = ~ mean(.x, na.rm = TRUE),
        sd = ~ sd(.x, na.rm = TRUE),
        min = ~ min(.x, na.rm = TRUE),
        max = ~ max(.x, na.rm = TRUE)
      )
    )
  )
```

Scatter plot comparing bill length and bill depth

```{r}
palmerpenguins::penguins %>%
  ggplot +
    aes(x = bill_length_mm, y = bill_depth_mm) +
    geom_point(alpha = 0.5) +
    scale_x_log10("Bill Length") +
    ylab("Bill Depth")
```

## 2.2

Sample size of population & body mass categorized by species

```{r}
palmerpenguins::penguins %>% # BMW: select() was unecessary here. 
  group_by(species) %>%
  summarize(meanMass = mean(body_mass_g, na.rm = TRUE),
            rows = n())
```

Bar chart comparing body mass among different species of penguins

```{r}
# options(scipen = 999) # BMW: Why is this here?
palmerpenguins::penguins %>%
  ggplot +
    aes(x = species, y = body_mass_g) +
    # geom_bar(stat="identity", width = 0.5) # BMW: geom_bar() isn't really appropriate here. This plot shows the total (sum) of body mass across the 3 species. Probably not what you wanted? Better to show (1) the actual data points and (2) a summary like a boxplot
  geom_jitter(aes(color = species), height = 0, width = .2, alpha = .5) +
  geom_boxplot(fill = "transparent")
```

# Bonus Exercise

The following code was provided 

```{r}
filter(gapminder, country == c("Rwanda", "Afghanistan"))
```

While the goal of this code is to get all data for Rwanda and Afghanistan, it does not work. The "==" function alternates the search for Rwanda and Afghanistan; it does not search for these countries simultaneously. 

To accomplish the intended goal, one must use the %in% function instead

```{r}
filter(gapminder, country %in% c("Rwanda", "Afghanistan"))
```

This now lists all of the data for Rwanda and Afghanistan.

<!-- BMW: very nice! -->
