---
title: "Homework 2"
author: "Samruddhi Shinde"
date: "2/7/2021"
output:
  html_document: default
  github_document: default
---
#Exercise 1

##1.1 

Loading in packages needed for assignments
```{r}
library(tidyverse)
library(gapminder)
```

Filter data set to show 3 countries (Mexico, Pakistan, & Zimbabwe) from the 1970s
```{r}
gapminder %>%
  filter(country %in% c("Mexico","Pakistan", "Zimbabwe") & year %in% c(1970:1979))
```

##1.2

Select country and gdpPercap from filtered dataset
```{r}
gapminder %>%
  filter(country %in% c("Mexico","Pakistan", "Zimbabwe") & year %in% c(1970:1979)) %>%
  select(country, gdpPercap)
```

##1.3 

Create new variable for thr change in life expectancy
```{r}
gapminder %>%
  mutate(change_in_lifeExp = lifeExp - lag(lifeExp)) %>%
  filter(change_in_lifeExp<0)
```

##1.4

Filter gapminder dataset to show the max GDP per capita for each country
```{r}
gapminder %>%
  group_by(country) %>%
  filter(gdpPercap == max(gdpPercap))
```

##1.5

Scatter plot of Canada's Life expectancy vs GDP per capita
```{r}
gapminder %>%
  filter(country == "Canada") %>%
  ggplot +
    aes(x = gdpPercap, y = lifeExp) +
    geom_point() + 
    scale_x_log10("GDP per capita", labels = scales::dollar_format()) +
    ylab("Life Expectancy") +
    ggtitle("Canada's GDP per Capita vs Life Expectancy")
```

#Excerise 2

##2.1

Loading in packages for exercise 

```{r}
library(palmerpenguins)
library(tidyverse)
```

Summarize bill length and bill depth
```{r}
palmerpenguins::penguins %>%
   summarize(
  across(c(bill_length_mm, bill_depth_mm),
  list(mean = ~ mean(.x, na.rm = TRUE),
      sd = ~ sd(.x, na.rm = TRUE),
      min = ~ min(.x, na.rm = TRUE),
      max = ~ max(.x, na.rm = TRUE))))
```

Scatter plot comparing bill length and bill depth
```{r}
palmerpenguins::penguins %>%
  ggplot +
    aes(x = bill_length_mm, y = bill_depth_mm) +
    geom_point(alpha = 0.5) +
    scale_x_log10("Bill Length") +
    ylab("Bill Depth")
```

##2.2

Sample size of population & body mass categorized by species
```{r}
palmerpenguins::penguins %>%
  select(species, body_mass_g) %>%
  group_by(species) %>%
    summarize(meanMass = mean(body_mass_g, na.rm = TRUE),
              rows = n())
```

Bar chart comparing body mass among different species of penguins
```{r}
options(scipen = 999)
palmerpenguins::penguins %>%
  ggplot +
    aes(x = species, y = body_mass_g) +
    geom_bar(stat="identity", width = 0.5)
```

#Bonus Exercise

The following code was provided 
```{r}
filter(gapminder, country == c("Rwanda", "Afghanistan"))
```

While the goal of this code is to get all data for Rwanda and Afghanistan, it does not work. The "==" function alternates the search for Rwanda and Afghanistan; it does not search for these countries simultaneously. 

To accomplish the intended goal, one must use the %in% function instead
```{r}
filter(gapminder, country %in% c("Rwanda", "Afghanistan"))
```
This now lists all of the data for Rwanda and Afghanistan.