---
title: "Homework 2"
author: "Samruddhi Shinde"
date: "2/7/2021"
output:
  html_document: default
  github_document: default
---
#Exercise 1

##1.1 

Loading in packages needed for assignments
```{r}
library(tidyverse)
library(gapminder)
```

Filter data set to show 3 countries (Mexico, Pakistan, & Zimbabwe) from the 1970s
```{r}
gapminder %>%
  filter(country %in% c("Mexico","Pakistan", "Zimbabwe") & year %in% c(1970:1979))
```

##1.2

Select country and gdpPercap from filtered dataset
```{r}
gapminder %>%
  filter(country %in% c("Mexico","Pakistan", "Zimbabwe") & year %in% c(1970:1979)) %>%
  select(country, gdpPercap)
```

##1.3 

Create new variable for thr change in life expectancy
```{r}
gapminder %>%
   mutate(change_in_lifeExp = lifeExp - lag(lifeExp))
```

##1.4

Filter gapminder dataset to show the max GDP per capita for each country
```{r}
gapminder %>%
  group_by(country) %>%
  summarize(max(gdpPercap))
```

##1.5

Scatter plot of Canada's Life expectancy vs GDP per capita
```{r}
gapminder %>%
  filter(country == "Canada") %>%
  ggplot +
    aes(x = gdpPercap, y = lifeExp) +
    geom_point() + 
    scale_x_log10("GDP per capita", labels = scales::dollar_format()) +
    ylab("Life Expectancy") +
    theme_bw()
```

