# Homework 03

You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.

```{r}
dictionary <- readr::read_csv("green_dictionary.csv")
green_data <- readr::read_csv("green_data.csv")
library(tidyverse)
```

For your assignment, do the following.

  1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). 
     Is anything unusual?
     
Based on the printed summary, there are -99 values in the dataset. These values need to be recoded as missing

```{r}
green_data %>%
  summary()
```
  
The na_if function coverts values to "NA"

```{r}
green_data <- green_data %>%
  na_if("-99")
```
  
The new set of data does not have any -99 values
  
```{r}
green_data %>%
  summary()
```  

  2. Compute total scores for the four scales. 
     Recode variables as needed.

```{r}
reversed <- c("green2","comp6","comp7","comp8","comp9","comp10","intel7","intel8","intel9","intel10","open7","open8","open9","open10")

green_data <- green_data %>%
  mutate(
    across(all_of(reversed),
           ~ recode(.x, "1" = 5, "2" = 4, "4" = 2, "5" = 1),
                           .names = "{.col}r"))
```

```{r}
green_data <- 
  green_data %>% 
  rowwise() %>% 
  mutate(
    green_tot = mean(c(green1, green2r, green3, green4, green5), na.rm = TRUE),
    comp_tot = mean(c(comp1, comp2, comp3, comp4, comp5, comp6r, comp7r, comp8r, comp9r, comp10r), na.rm = TRUE),
    intel_tot = mean(c(intel1, intel2, intel3, intel4, intel5, intel6, intel7r, intel8r, intel9r, intel10r), na.rm = TRUE),
    open_tot = mean(c(open1, open2, open3, open4, open5, open6, open7r, open8r, open9r, open10r), na.rm = TRUE))
```

  3. Rescale the variables so that they go from 0-100 instead of the original range.
     Name the recaled variables `*_pomp`.
     
```{r}
green_data <- 
  green_data %>% 
  rowwise() %>% 
  mutate(
    across(c(green1:open10r),
    ~ recode(.x, "1" = 0, "2" = 25, "3" = 50, "4" = 75, "5" = 100),
    .names = "{.col}_pomp"))

green_data <- 
  green_data %>% 
  rowwise() %>% 
  mutate(
    green_pomp = sum(c(green1_pomp,green2r_pomp,green3_pomp,green4_pomp,green5_pomp), na.rm = TRUE),
    comp_pomp = sum(c(comp1_pomp,comp2_pomp,comp3_pomp,comp4_pomp,comp5_pomp,comp6r_pomp,comp7r_pomp, comp8r_pomp,comp9r_pomp,comp10r_pomp), na.rm = TRUE),
    intel_pomp = sum(c(intel1_pomp,intel2_pomp,intel3_pomp,intel4_pomp,intel5_pomp,intel6_pomp,intel7r_pomp, intel8r_pomp,intel9r_pomp,intel10r_pomp), na.rm = TRUE),
    open_pomp = sum(c(open1_pomp,open2_pomp,open3_pomp,open4_pomp,open5_pomp,open6_pomp,open7r_pomp, open8r_pomp,open9r_pomp,open10r_pomp), na.rm = TRUE)) 
```

```{r}
green_data %>%
  print(green_pomp)
```


  4. Make plots that illustrate the distributions of the 4 POMP-scored variables.
  
```{r}
green_data %>%
  aes(x= green_pomp) +
  geom_bar()
```
  
  
  5. Make scatterplots showing the relationships between **green reputation** and each personality trait.
     Include trend lines for **students** and **non-students**.
     What do these plots show?
  6. Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).
  7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
  
In your assignment, prepare an RMarkdown file that includes both the coding and (for 4-7) narrative descriptions of your results.
