# Homework 03

You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.

```{r}
dictionary <- readr::read_csv("green_dictionary.csv")
green_data <- readr::read_csv("green_data.csv")
library(tidyverse)
```

For your assignment, do the following.

  1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). 
     Is anything unusual?
     
Based on the printed summary, there are -99 values in the dataset. These values need to be recoded as missing

```{r}
green_data %>%
  summary()
```
  
The na_if function coverts values to "NA"

```{r}
green_data <- green_data %>%
  na_if("-99")
```
  
The new set of data does not have any -99 values
  
```{r}
green_data %>%
  summary()
```  

  2. Compute total scores for the four scales. 
     Recode variables as needed.

```{r}
reversed <- dictionary %>%
  filter(Keying == -1) %>%
  pull(Item)

green_data <- green_data %>%
  mutate(
    across(all_of(reversed),
           ~ recode(.x, "1" = 5, "2" = 4, "4" = 2, "5" = 1),
           .names = "{.col}r"))

print(green_data)
```

```{r}
green_data <- green_data %>% 
  rowwise() %>% 
  mutate(
    .id = id,
    green_total = mean(c(green1, green2r, green3, green4, green5), na.rm = TRUE),
    comp_total = mean(c(comp1, comp2, comp3, comp4, comp5, comp6r, comp7r, comp8r, comp9r, comp10r), na.rm = TRUE),
    intel_total = mean(c(intel1, intel2, intel3, intel4, intel5, intel6, intel7r, intel8r, intel9r, intel10r), na.rm = TRUE),
    open_total = mean(c(open1, open2, open3, open4, open5, open6, open7r, open8r, open9r, open10r), na.rm = TRUE))
```

  3. Rescale the variables so that they go from 0-100 instead of the original range.
     Name the recaled variables `*_pomp`.
     
```{r}
green_data <- 
  green_data %>% 
  rowwise() %>% 
  mutate(
    across(c(green1:open10r),
    ~ recode(.x, "1" = 0, "2" = 25, "3" = 50, "4" = 75, "5" = 100),
    .names = "{.col}_pomp"))

green_data <- 
  green_data %>% 
  rowwise() %>% 
  mutate(
    green_pomp = sum(c(green1_pomp,green2r_pomp,green3_pomp,green4_pomp,green5_pomp), na.rm = TRUE),
    comp_pomp = sum(c(comp1_pomp,comp2_pomp,comp3_pomp,comp4_pomp,comp5_pomp,comp6r_pomp,comp7r_pomp, comp8r_pomp,comp9r_pomp,comp10r_pomp), na.rm = TRUE),
    intel_pomp = sum(c(intel1_pomp,intel2_pomp,intel3_pomp,intel4_pomp,intel5_pomp,intel6_pomp,intel7r_pomp, intel8r_pomp,intel9r_pomp,intel10r_pomp), na.rm = TRUE),
    open_pomp = sum(c(open1_pomp,open2_pomp,open3_pomp,open4_pomp,open5_pomp,open6_pomp,open7r_pomp, open8r_pomp,open9r_pomp,open10r_pomp), na.rm = TRUE)) 
```

```{r}
green_data %>%
  summary(green_pomp)
```


  4. Make plots that illustrate the distributions of the 4 POMP-scored variables.
  
```{r}
ggplot(green_data) +
  aes(x = green_pomp) +
  geom_bar() +
  theme_bw()

ggplot(green_data) +
  aes(x = comp_pomp) +
  geom_bar() +
  theme_bw()

ggplot(green_data) +
  aes(x = intel_pomp) +
  geom_bar() +
  theme_bw()

ggplot(green_data) +
  aes(x = open_pomp) +
  geom_bar() +
  theme_bw()
```

  5. Make scatterplots showing the relationships between **green reputation** and each personality trait.
     Include trend lines for **students** and **non-students**.
     What do these plots show?
     
```{r}
green_data %>% 
  filter(!is.na(student)) %>% 
  ggplot() +
  aes(y = comp_pomp,
      x = green_pomp,
      group = student,
      color = student,
      fill = student) +
  geom_jitter()

green_data %>% 
  filter(!is.na(student)) %>% 
  ggplot() +
  aes(y = intel_pomp,
      x = green_pomp,
      group = student,
      color = student,
      fill = student) +
  geom_jitter()
  
green_data %>% 
  filter(!is.na(student)) %>% 
  ggplot() +
  aes(y = open_pomp,
      x = green_pomp,
      group = student,
      color = student,
      fill = student) +
  geom_jitter()
```
     
  6. Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).
  
```{r}

```
  
  
  7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
  
```{r}
summary_green <- green_data %>% 
  na.omit() %>% 
  group_by(student) %>% 
  summarize(green_mean = mean(green_pomp),
            green_sd = sd(green_pomp),
            green_median = median(green_pomp),
            green_min = min(green_pomp),
            green_max = max(green_pomp),
            comp_mean = mean(comp_pomp),
            comp_sd = sd(comp_pomp),
            comp_median = median(comp_pomp),
            comp_min = min(comp_pomp),
            comp_max = max(comp_pomp),
            intel_mean = mean(intel_pomp),
            intel_sd = sd(intel_pomp),
            intel_median = median(intel_pomp),
            intel_min = min(intel_pomp),
            intel_max = max(intel_pomp),
            open_mean = mean(open_pomp),
            open_sd = sd(open_pomp),
            open_median = median(open_pomp),
            open_min = min(open_pomp),
            open_max = max(open_pomp))

print(summary_green)
```
  
  
In your assignment, prepare an RMarkdown file that includes both the coding and (for 4-7) narrative descriptions of your results.
