---
title: "Homework 3"
author: "Sam Shinde"
date: "2/24/2021"
output: 
  github_document: default
  html_document: default
---

# Homework 03

You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.

```{r}
dictionary <- readr::read_csv("green_dictionary.csv")
green_data <- readr::read_csv("green_data.csv")
library(tidyverse)
library(ggdist)
```

For your assignment, do the following.

  1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). 
     Is anything unusual?
     
Based on the printed summary, there are -99 values in the dataset. These values need to be recoded as missing

```{r}
green_data %>%
  summary()
```
  
The na_if function coverts values to "NA"

```{r}
green_data <- green_data %>%
  na_if("-99")
```
  
The new set of data does not have any -99 values
  
```{r}
green_data %>%
  summary()
```  

  2. Compute total scores for the four scales. 
     Recode variables as needed.

Some of the items are reverse coded, so they must be recoded. Additionally, the student variable needs to be recorded as a factor.

```{r}
reversed <- dictionary %>%
  filter(Keying == -1) %>%
  pull(Item)

green_data <- green_data %>%
  mutate(
    across(all_of(reversed),
           ~ recode(.x, "1" = 5, "2" = 4, "4" = 2, "5" = 1),
           .names = "{.col}r"))

green_data$student <- recode_factor(green_data$student, '1' = "Non-student", '2' = "Student")

print(green_data)
```

The following formulas calculate the average mean of the total scores in each category

```{r}
green_data <- green_data %>% 
  rowwise() %>% 
  mutate(
    .id = id,
    green_total = mean(c(green1, green2r, green3, green4, green5), na.rm = TRUE),
    comp_total = mean(c(comp1, comp2, comp3, comp4, comp5, comp6r, comp7r, comp8r, comp9r, comp10r), na.rm = TRUE),
    intel_total = mean(c(intel1, intel2, intel3, intel4, intel5, intel6, intel7r, intel8r, intel9r, intel10r), na.rm = TRUE),
    open_total = mean(c(open1, open2, open3, open4, open5, open6, open7r, open8r, open9r, open10r), na.rm = TRUE))
```

  3. Rescale the variables so that they go from 0-100 instead of the original range.
     Name the recaled variables `*_pomp`.
     
The score values must be recoded to be on a 0-100 scale. Then we can calculate the mean for each category.
     
```{r}
green_data <- 
  green_data %>% 
  rowwise() %>% 
  mutate(
    across(c(green1:open10r),
    ~ recode(.x, "1" = 0, "2" = 25, "3" = 50, "4" = 75, "5" = 100),
    .names = "{.col}_pomp"))

green_data <- 
  green_data %>% 
  rowwise() %>% 
  mutate(
    green_pomp = mean(c(green1_pomp,green2r_pomp,green3_pomp,green4_pomp,green5_pomp), na.rm = TRUE),
    comp_pomp = mean(c(comp1_pomp,comp2_pomp,comp3_pomp,comp4_pomp,comp5_pomp,comp6r_pomp,comp7r_pomp, comp8r_pomp,comp9r_pomp,comp10r_pomp), na.rm = TRUE),
    intel_pomp = mean(c(intel1_pomp,intel2_pomp,intel3_pomp,intel4_pomp,intel5_pomp,intel6_pomp,intel7r_pomp, intel8r_pomp,intel9r_pomp,intel10r_pomp), na.rm = TRUE),
    open_pomp = mean(c(open1_pomp,open2_pomp,open3_pomp,open4_pomp,open5_pomp,open6_pomp,open7r_pomp, open8r_pomp,open9r_pomp,open10r_pomp), na.rm = TRUE)) 
```

  4. Make plots that illustrate the distributions of the 4 POMP-scored variables.

Environmental consciousness is normally distributed. Compassion and openness are skewed right. Intelligence has a bimodal distribution.

```{r}
ggplot(green_data) +
  aes(x = green_pomp) +
  geom_bar() +
  theme_bw()

ggplot(green_data) +
  aes(x = comp_pomp) +
  geom_bar() +
  theme_bw()

ggplot(green_data) +
  aes(x = intel_pomp) +
  geom_bar() +
  theme_bw()

ggplot(green_data) +
  aes(x = open_pomp) +
  geom_bar() +
  theme_bw()
```

  5. Make scatterplots showing the relationships between **green reputation** and each personality trait.
     Include trend lines for **students** and **non-students**.
     What do these plots show?
     
Environmental consciousness is positively correlated with openness, intelligence, and compassion for both students and non-students. However, students reported higher levels of compassion and openness compared to non-students.
     
```{r}
green_data %>% 
  filter(!is.na(student)) %>% 
  ggplot() +
  aes(y = comp_pomp,
      x = green_pomp,
      group = student,
      color = student,
      fill = student) +
  geom_jitter() +
  geom_smooth(method = "lm")

green_data %>% 
  filter(!is.na(student)) %>% 
  ggplot() +
  aes(y = intel_pomp,
      x = green_pomp,
      group = student,
      color = student,
      fill = student) +
  geom_jitter() +
  geom_smooth(method = "lm")
  
green_data %>% 
  filter(!is.na(student)) %>% 
  ggplot() +
  aes(y = open_pomp,
      x = green_pomp,
      group = student,
      color = student,
      fill = student) +
  geom_jitter() +
  geom_smooth(method = "lm")
```
     
  6. Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).
  
Student responses appear to have a normal distribution. Non-student reponses appear to have a bimodal distribution.
  
```{r}
green_data %>%
  filter(!is.na(student)) %>% 
  ggplot() +
    aes(y = student, x = green_pomp, na.omit, color = student) +
    geom_jitter(height = 0.2) +
    geom_boxplot(alpha = .5,
               width = .1,
               size = .5) +
    ggdist::stat_slab(height = .3,
                      position = position_nudge(y = .4))
```
  
  
  7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
  
On average, students report higher levels of environmental conciousness and intelligence compared to non-students. They also report lower levels of compassion and openness compared to non-students.
  
```{r}
summary_green <- green_data %>% 
  na.omit() %>% 
  group_by(student) %>% 
  summarize(green_mean = mean(green_pomp),
            green_sd = sd(green_pomp),
            green_median = median(green_pomp),
            green_min = min(green_pomp),
            green_max = max(green_pomp),
            comp_mean = mean(comp_pomp),
            comp_sd = sd(comp_pomp),
            comp_median = median(comp_pomp),
            comp_min = min(comp_pomp),
            comp_max = max(comp_pomp),
            intel_mean = mean(intel_pomp),
            intel_sd = sd(intel_pomp),
            intel_median = median(intel_pomp),
            intel_min = min(intel_pomp),
            intel_max = max(intel_pomp),
            open_mean = mean(open_pomp),
            open_sd = sd(open_pomp),
            open_median = median(open_pomp),
            open_min = min(open_pomp),
            open_max = max(open_pomp))

tibble(summary_green)
```
