# Homework 03

You will analyze data looking at the relationship between **green reputation** and three personality traits--**compassion**, **intellectual curiosity**, and **openness to experiences**.
The dataset includes data from **students** and **non-students**.

```{r}
dictionary <- readr::read_csv("green_dictionary.csv")
green_data <- readr::read_csv("green_data.csv")
library(tidyverse)
```

For your assignment, do the following.

  1. Inspect the item responses (e.g., with graphs or by summarizing distinct values). 
     Is anything unusual?
     
Based on the printed summary, there are -99 values in the dataset. These values need to be recoded as missing

```{r}
green_data %>%
  summary()
```
  
The na_if function coverts values to "NA"

```{r}
new_green_data <- green_data %>%
  na_if("-99")
```
  
The new set of data does not have any -99 values
  
```{r}
new_green_data %>%
  summary()
```  

  2. Compute total scores for the four scales. 
     Recode variables as needed.

```{r}
reversed <- c("green2","comp6","comp7","comp8","comp9","comp10","intel7","intel8","intel9","intel10","open7","open8","open9","open10")

new_green_data <- new_green_data %>%
  mutate(
    across(all_of(reversed),
           ~ recode(.x, "1" = 5, "2" = 4, "4" = 2, "5" = 1),
                           .names = "{.col}r"))
```

```{r}
new_green_data <- 
  new_green_data %>% 
  rowwise() %>% 
  mutate(green_tot = mean(c(green1, green2r, green3, green4, green5), na.rm = TRUE),
         comp_tot = mean(c(comp1, comp2, comp3, comp4, comp5, comp6r, comp7r, comp8r, comp9r, comp10r), 
                         na.rm = TRUE),
         intel_tot = mean(c(intel1, intel2, intel3, intel4, intel5, intel6, intel7r, intel8r, intel9r, intel10r),
                          na.rm = TRUE),
         open_tot = mean(c(open1, open2, open3, open4, open5, open6, open7r, open8r, open9r, open10r), 
                         na.rm = TRUE))
```

  3. Rescale the variables so that they go from 0-100 instead of the original range.
     Name the recaled variables `*_pomp`.
     
```{r}
new_green_data <- 
  new_green_data %>% 
  rowwise() %>% 
  mutate(
```
     
  4. Make plots that illustrate the distributions of the 4 POMP-scored variables.
  5. Make scatterplots showing the relationships between **green reputation** and each personality trait.
     Include trend lines for **students** and **non-students**.
     What do these plots show?
  6. Compare **green reputation** for students and non-students using a **rainfall plot** (bar + density + data points).
  7. Compute a summary table of means, SDs, medians, minima, and maxima for the four total scores for students and non-students.
  
In your assignment, prepare an RMarkdown file that includes both the coding and (for 4-7) narrative descriptions of your results.
