---
title: "2/9/2021"
author: "Samruddhi Shinde"
date: "2/9/2021"
output: html_document
---

1. Use the `psych::bfi` dataset.

```{r}
library(psych)
library(tidyverse)
```

2. Compute mean scores for each of the Big Five traits for each person.

```{r}
psych::bfi %>%
  rowwise() %>%
  mutate(Agree_total = mean(c_across(A1:A5), na.rm = TRUE),
         Conc_total = mean(c_across(C1:C5), na.rm = TRUE),
         Open_total = mean(c_across(O1:O5), na.rm = TRUE),
         Neuro_total = mean(c_across(N1:N5), na.rm = TRUE),
         Extra_total = mean(c_across(E1:E5), na.rm = TRUE)) %>%
  select(Agree_total, Conc_total, Open_total, Neuro_total, Extra_total)
  
```

3. Keep just Big Five scores, gender, age, and education.

```{r}
psych::bfi %>%
  rowwise() %>%
  mutate(Agree_total = mean(c_across(A1:A5), na.rm = TRUE),
         Conc_total = mean(c_across(C1:C5), na.rm = TRUE),
         Open_total = mean(c_across(O1:O5), na.rm = TRUE),
         Neuro_total = mean(c_across(N1:N5), na.rm = TRUE),
         Extra_total = mean(c_across(E1:E5), na.rm = TRUE)) %>%
  select(Agree_total, Conc_total, Open_total, Neuro_total, Extra_total, age, education, gender)
```

4. Summarize the mean, standard deviation, minimum, and maximum values for the Big Five scores separately by gender groups.

```{r}
psych::bfi %>%
  group_by(gender) %>%
    summarize(
      meanA = mean(c_across(A1:A5), na.rm = TRUE),
      sdA = sd(c_across(A1:A5), na.rm = TRUE),
      minA = min(c_across(A1:A5), na.rm = TRUE),
      maxA = max(c_across(A1:A5), na.rm = TRUE),
      meanO = mean(c_across(O1:O5), na.rm = TRUE),
      sdO = sd(c_across(O1:O5), na.rm = TRUE),
      minO = min(c_across(O1:O5), na.rm = TRUE),
      maxO = max(c_across(O1:O5), na.rm = TRUE),
      meanE = mean(c_across(E1:E5), na.rm = TRUE),
      sdE = sd(c_across(E1:E5), na.rm = TRUE),
      minE = min(c_across(E1:E5), na.rm = TRUE),
      maxE = max(c_across(E1:E5), na.rm = TRUE),
      meanN = mean(c_across(N1:N5), na.rm = TRUE),
      sdN = sd(c_across(N1:N5), na.rm = TRUE),
      minN = min(c_across(N1:N5), na.rm = TRUE),
      maxN = max(c_across(N1:N5), na.rm = TRUE),
      meanC = mean(c_across(C1:C5), na.rm = TRUE),
      sdC = sd(c_across(C1:C5), na.rm = TRUE),
      minC = min(c_across(C1:C5), na.rm = TRUE),
      maxC = max(c_across(C1:C5), na.rm = TRUE))
```

```{r}
psych::bfi %>%
  group_by(gender) %>%
    summarize(c(A1:O5)
              list(mean = ~ mean(.x, na.rm = TRUE),
                   sd = ~ sd(.x, na.rm = TRUE),
                   min = ~ min(.x, na.rm = TRUE),
                   max = ~ max(.x, na.rm = TRUE)))
```


5. Summarize the mean, standard deviation, minimum, and maximum values for the Big Five scores separately by educational level groups.

```{r}
psych::bfi %>%
  group_by(education) %>%
    summarize(
      meanA = mean(c_across(A1:A5), na.rm = TRUE),
      sdA = sd(c_across(A1:A5), na.rm = TRUE),
      minA = min(c_across(A1:A5), na.rm = TRUE),
      maxA = max(c_across(A1:A5), na.rm = TRUE),
      meanO = mean(c_across(O1:O5), na.rm = TRUE),
      sdO = sd(c_across(O1:O5), na.rm = TRUE),
      minO = min(c_across(O1:O5), na.rm = TRUE),
      maxO = max(c_across(O1:O5), na.rm = TRUE),
      meanE = mean(c_across(E1:E5), na.rm = TRUE),
      sdE = sd(c_across(E1:E5), na.rm = TRUE),
      minE = min(c_across(E1:E5), na.rm = TRUE),
      maxE = max(c_across(E1:E5), na.rm = TRUE),
      meanN = mean(c_across(N1:N5), na.rm = TRUE),
      sdN = sd(c_across(N1:N5), na.rm = TRUE),
      minN = min(c_across(N1:N5), na.rm = TRUE),
      maxN = max(c_across(N1:N5), na.rm = TRUE),
      meanC = mean(c_across(C1:C5), na.rm = TRUE),
      sdC = sd(c_across(C1:C5), na.rm = TRUE),
      minC = min(c_across(C1:C5), na.rm = TRUE),
      maxC = max(c_across(C1:C5), na.rm = TRUE))
```
